LaTeX Template for a Scientific Paper

### 2017-01-30 report/paper.tex
added related work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}\label{sec:sota}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Related Work section contains an analysis of the most relevant related literature (remarking the shortcomings that are addressed in your work)

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}\label{sec:sota}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A good introduction about the SDN can be the  "Simulation in an SDN network scenario using the
POX Controller" where has been presented the SDN environment and the mininet simulation
tool that creates a topology where to simulate the switches, the traffic between hosts and
allow the controller to communicate with the switches. The work presented in
"Efficient topology discovery in OpenFlow-based Software Defined Networks" by F. Pakzad [put cit]
has been implemented to improve the controller speed and efficiency as it make it more reactive.
The introduction to the statistics power in a SDN network using the OpenFlow protocol has been found
in the paper called "Getting traffic statistics from network devices in an
SDN environment using OpenFlow" by D.J. Hamad & others. [ put note here]
For traffic analysis we haven't found any paper describing the characteristics of
some types of flows, so we used our PCs to sniff the traffic. Traffic analysis will be discussed in section \ref{sec:symo}.

@@

\subsection{Traffic analysis}
We used laptop connected via
GigabitEthernet interface and Ethernet cable cat.5a to receive the traffic from the destination host.
Our laptop has been connected via Wi-Fi to our access point via protocol 802.11n.
No other traffic sources were active during the testing, so the router was handling only
the traffic from laptop when sniffing traffic. The connection used was an ADSL2+ via copper.
We did 3 type of traffic analysis: Gaming traffic, Skype® and torrent traffic. We analyzed
#Mb for the gaming traffic, #Mb for the VoIP traffic and 3GB for the torrent traffic.
The analysis involved the average number of packets per second, the packet size, the protocol (TCP or UDP)
